---
title: "Alcohol vs Seat choice"
author: "Andrew Valles Tovar"
date: "Spring 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

What this fancy box plot shows are three categories of people's seating, front, middle, and back. What the notches on the boxes represent are confidence intervals around the median. Since the notches on the box labeled back do not overlap the front or middle boxes, there is strong evidence that the median differs. It's possible to hypothesize that the people seated in the back consume a higher average of alcohol than those seated in the front or middle.

## Numerical Summarys 

## Inferential Tests

## Conclusions


