---
title: "Alcohol vs Seat choice"
author: "Andrew Valles Tovar"
date: "Spring 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

What this fancy box plot shows are three categories of people's seating, front, middle, and back. What the notches on the boxes represent are confidence intervals around the median. Since the notches on the box labeled back do not overlap the front or middle boxes, there is strong evidence that the median differs. It's possible to hypothesize that the people seated in the back consume a higher average of alcohol than those seated in the front or middle.

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=davisdata)
```

The numerical data shows those who are seated in the back drank an average of 9 drinks. 9 drinks is 9 times than the average of those who sat in the front, and 3 times more than those seated in the middle. The Q1, Q3, and the median for people seated in the back are substantially higher than those seated in the front and middle.

## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The inferential test proposes there is no difference on the amount of alcohol consumed between the front, middle, and back seats, but only at a 0.000116% chance. The chance of that happening is incredibly slim. Therefore, it is safe to reject the idea of there being no difference on the amount of alcohol consumed between the 3 seating positions.

```{r}
plot(TukeyHSD(model1))
```

The TukeyHSD test here shows that there is a difference on alcohol consumed between the front and back positions and middle and back positions. Because the front/back and middle/back categories does not cross over the confidence level at 0, we are able to determine that there is a difference on alcohol consumed. The middle/front category does cross over the confidence level, meaning that there is no difference on the alcohol consumed for that category.

## Conclusions
In summary, the data shown from the fancy box plot, numerical summary, and inferential data clearly shows that the people seated in the back consumed a much higher average amount of alcohol compared to those seated in the front or middle. The inferential data shows that it is possible for there being no difference on the amount of alcohol consumed for the 3 seating positions, but only at a astronomical small chance of 0.000116%. The result for this data is people who are seated in the back consume more alcohol than the front and middle positions.

